Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-06-03 analysis/paper/shceof.Rmd
Arregla leer ERSST

```{r sst}
sst <- ERSST() %>%
  readRDS() %>% 
  .[season(time) == "SON"] %>%
  normalise_coords() %>%
  .[, w := season_weights(time)] %>% 
  .[, .(t = mean(t*w)), by = .(lon, lat, time = seasonally(time))]
```

>>>>

```{r sst}
sst <- ERSST() %>%
  fread() %>% 
  .[season(time) == "SON"] %>%
  normalise_coords() %>%
  .[, w := season_weights(time)] %>% 
  .[, .(t = mean(t*w)), by = .(lon, lat, time = seasonally(time))]
```
